The Holy Hand Grenade of Antioch

### 2020-02-22 draft-camelot-holy-grenade.tex
feat: fix quotes

The menagerie of beasts and artefacts depicted in RFC8140
may be usefully supplemented by other renowned figures of
Internet and more general lore. This document extends the
menagerie to the seminal fable of the
"Holy Hand Grenade of Antioch", as depicted in the
Monty Python film "Monty Python and the Holy Grail",
as well as "Spamalot", the musical inspired by the movie.

\begin{note}
  \mn{remove-in-rfc=false}
  \caption{Spamalot}
  The relevance of the musical "Spamalot" to Internet lore should be
  obvious to the reader; but in case of doubt, see also
  Section 1 ("\textbf{What is Spam?}") of RFC2635.
\end{note}

@@

The key words "\textbf{MUST}", "\textbf{MUST NOT}", "\textbf{REQUIRED}", "\textbf{SHALL}",
"\textbf{SHALL NOT}", "\textbf{SHOULD}", "\textbf{SHOULD NOT}", "\textbf{RECOMMENDED}",
"\textbf{NOT RECOMMENDED}", "\textbf{MAY}", and "\textbf{OPTIONAL}" in this document
are to be interpreted as described in BCP 14 \mncite{RFC2119} \mncite{RFC8174}
when, and only when, they appear in all capitals, as shown here.

@@

\begin{quote}
  \mn{attribution="A. Farrel"}
  Although the RFC Editor has recently dragged the IETF kicking and
  screaming into the twentieth century [RFC7990] [RFC7996], there is a
  yearning among all right-thinking Internet architects to "keep it
  simple" and to return to the olden days when pigs could be given
  thrust without anyone taking undue offence.
\end{quote}

@@

\begin{description}
  \item[Trojan Rabbit]
    In their siege of the French-occupied castle which may already
    contain an instance of the Grail, Sir Bedevere the Wise proposes to
    use a Trojan Rabbit to infiltrate the castle, with a raiding party
    to take the French "not only by surprise, but totally unarmed."

@@

"Here may be found the last words of Joseph~of Arimathea.
He who is valiant and pure of spirit may find the Holy Grail
in the castle of --- Aaaargh."
\end{quote}

>>>>

The menagerie of beasts and artefacts depicted in RFC8140
may be usefully supplemented by other renowned figures of
Internet and more general lore. This document extends the
menagerie to the seminal fable of the
``Holy Hand Grenade of Antioch'', as depicted in the
Monty Python film ``Monty Python and the Holy Grail'',
as well as ``Spamalot'', the musical inspired by the movie.

\begin{note}
  \mn{remove-in-rfc=false}
  \caption{Spamalot}
  The relevance of the musical ``Spamalot'' to Internet lore should be
  obvious to the reader; but in case of doubt, see also
  Section 1 (``\textbf{What is Spam?}'') of RFC2635.
\end{note}

@@

The key words ``\textbf{MUST}'', ``\textbf{MUST NOT}'', ``\textbf{REQUIRED}'', ``\textbf{SHALL}'',
``\textbf{SHALL NOT}'', ``\textbf{SHOULD}'', ``\textbf{SHOULD NOT}'', ``\textbf{RECOMMENDED}'',
``\textbf{NOT RECOMMENDED}'', ``\textbf{MAY}'', and ``\textbf{OPTIONAL}'' in this document
are to be interpreted as described in BCP 14 \mncite{RFC2119} \mncite{RFC8174}
when, and only when, they appear in all capitals, as shown here.

@@

\begin{quote}
  \mn{attribution="A. Farrel"}
  Although the RFC Editor has recently dragged the IETF kicking and
  screaming into the twentieth century [RFC7990] [RFC7996], there is a
  yearning among all right-thinking Internet architects to ``keep it
  simple'' and to return to the olden days when pigs could be given
  thrust without anyone taking undue offence.
\end{quote}

@@

\begin{description}
  \item[Trojan Rabbit]
    In their siege of the French-occupied castle which may already
    contain an instance of the Grail, Sir Bedevere the Wise proposes to
    use a Trojan Rabbit to infiltrate the castle, with a raiding party
    to take the French ``not only by surprise, but totally unarmed.''

@@

``Here may be found the last words of Joseph~of Arimathea.
He who is valiant and pure of spirit may find the Holy Grail
in the castle of --- Aaaargh.''
\end{quote}
